Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-12-05 analysis/paper/paper.Rmd

<!-- one equal-sized paragraph for each of our three questions, with lots of recent, specific citations for each Q -->

>>>>

<!-- one equal-sized paragraph for each of our three questions, with lots of recent, specific citations for each Q

State the questions very clearly and give background into relevant literature:

 -  the population: that some relationship may exist between population as a cause of techno change: Torrence, Collard, Shennan

 - the way people used the landscape: changing mobility patterns due to risk management,  Kelly, Fitzhugh, Shott

 - the way people used sites: more fine-grained evidence about land use patterns long vs short term durations of site use Kuhn, Andresfsky, Hiscock
